\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-21 main.tex
minor edits

\paragraph{PDF polyglots} 
Having identified PDF as a particularly dangerous format, we perform
a novel in-depth study of
PDF-based injection and content smuggling attacks. 
Our findings expose new attack vectors, which we demonstrate both
conceptually and by a proof-of-concept web pages.

@@

\paragraph{Scenario}
The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describe how 
the attack proceed, from the infiltration of the origin, to the compromise of the victim.
The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 
The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to \emph{vulnerable.com}, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (1).
The \emph{attacker.com} site serves a page that embeds the content from \emph{vulnerable.com} (2). 
The attacker supplies polyglot syntax in the input to the vulnerable 
service, e.g. in the parameters of the request for the embedded content (3).
The \emph{vulnerable.com} service responds with content of the benign content type (4), but
the way it is embedded in the attackers page coerces the browser to interpret it as the malicious content type.
The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
hence leverage the credentials of the victim to further exploit the vulnerability.

>>>>

\paragraph{PDF polyglots} 
Having identified PDF as a particularly dangerous format, we perform
a novel in-depth study of
PDF-based injection and content smuggling attacks. 
Our findings expose new attack vectors, which we demonstrate both
conceptually and by proof-of-concept web pages.

@@

\paragraph{Scenario}
The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describes how 
the attack proceeds from the infiltration of the origin to the compromise of the victim.
The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 
The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to \emph{vulnerable.com}, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (1).
The \emph{attacker.com} site serves a page that embeds the content from \emph{vulnerable.com} (2). 
The attacker supplies polyglot syntax in the input to the vulnerable 
service, e.g. in the parameters of the request for the embedded content (3).
The \emph{vulnerable.com} service responds with content of the benign content type (4), but
the way it is embedded in the attackers page coerces the browser to interpret it as the malicious content type.
The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
hence leverage the credentials of the victim to further exploit the vulnerability.
